\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-10 latex/paper_sensores/paper.tex
a ver si anda

In the datasheets of the considered sensors(\cite{bib:acc_data} and \cite{bib:gyro_data}) the effect of nonlinearityis negligible since it represents the $\pm 0.5.\%$  of the full scale for the accelerometer and the $\pm 0.2\%$ for the gyroscope. Therefore we will not discuss any further on this issue.\\
%TODO Esto es medio turbio que sea despreciable... en realidad me da que no habría que despreciarlo. Capaz que es mejor esconder este punto.

In figure \ref{fig:ruido} we can observe that the electrical noise of the devices is typically 2 bits, this error (acording the datashets \cite{bib:acc_data} and \cite{bib:gyro_data})correspond to $7.8 mg$ and $0.14 ^{\circ}/s $.  
%TODO Cuando tengamos la gráfica ver bien cuanto es el ruido y a cuanto corresponde en la vida real. Tampoco se si es tan despreciable. Capaz que hay que decir que se usan muchas muestras normalmente y que variaciones aleatorias de cierta varianza no joden mucho. Pero ahora no me voy a poner a hacer eso xq tengo sueño.

\subsection{Accelerometer}
\subsection{Gyroscope}

>>>>

In the datasheets of the considered sensors(\cite{bib:acc_data} and \cite{bib:gyro_data}) the effect of nonlinearityis negligible since it represents the $\pm 0.5.\%$  of the full scale for the accelerometer and the $\pm 0.2\%$ for the gyroscope. Therefore we will not consider this effect and after the calibration we must verify that the error due to the nonlinear response is negligeable.\\
%TODO Al final hacer las cuentas para ver que es despreciable.

In figure \ref{fig:ruido} we can observe that the electrical noise of the devices is typically 2 bits, this error (according to the datashets \cite{bib:acc_data} and \cite{bib:gyro_data})correspond to $7.8 mg$ and $0.14 ^{\circ}/s $. The error is not biased, thus we not need to consider it, because several samples are used in any real application and the effect vanishes.\\

Based on the asumption that both sensors have a linear response and considering the non-orthogonality of the axis of the devices we are going to present a standard model for both sensors(see \cite{bib:calib_imu}, \cite{bib:kalman}, \cite{bib:calib_imu_dos}).

\subsection{Accelerometer}
Due to construction issues the sensibility axis of the device are generaly not orthogonals. Let $\mathbf{a}^a$ be the acceleration measured by the accelerometer and let $\mathbf{a}^p$.

\subsection{Gyroscope}
